Insurance choice, decision assistance, and insurer steering

### 2021-03-26 finals/lunch-and-learn/lunch-learn-202103.Rmd
fix scale of results figures
update slides

---
# Rating areas

@@

- Smoking
- Age
- Rating area
]

@@

- Subsidies available for households with incomes below 250% of the FPL
- At 150% of the FPL, larger subsidies are such that actuarial value of silver plans exceeds that of gold and platinum plans
- Gold and platinum plans dominated by silver plans for incomes $\leq$ 150% FPL

@@

.center[
  ![](../../figures/dominated_choice_regression.png)
]

>>>>

---
# Community rating rules

@@

- Smoking (not in CA)
- Age
- Rating area
]

@@

- Subsidies available for households with incomes below 250% of the FPL
- At 150% of the FPL, larger subsidies are such that actuarial value of silver plans exceeds that of gold and platinum plans
- Gold and platinum plans dominated by silver plans for incomes $\leq$ 150% FPL
- Gold plans dominated by silver plans for incomes between 150% and 200% FPL

@@

.center[
  ![:scale 50%](../../figures/dominated_choice_regression.png)
]
